~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\\

\noindent 
This work would not have been possible without the help from a large number of humans, and one dog.\\\\

First, I would like to thank my advisor, Mike Shaevitz, for helping me every step along the way for the past six years. From selecting me from the undergraduate candidate pool for the summer REU internship at Nevis working on the Double Chooz experiment to serving as the sponsor for my thesis defense, Mike has always been there for me. The advisor-student relationship is an important one, and I am incredibly fortunate to have landed in Mike's group. During my tenure as a graduate student, I always felt supported and welcomed, and I never felt afraid to ask a question, no matter how stupid I worried it was.\\

I would like to thank perhaps the most influential teacher in my life, Hugon Karwowski. He taught me introductory mechanics and electromagnetism during my first year of undergraduate study at the University of North Carolina, and his passion for physics and creativity in creating test questions (``David Kaleko sits atop a frictionless ramp slanting down towards a pool filled with sharks. How long until he suffers a gruesome death?'') is what truly spawned a love of physics within me. Throughout my TAing and private tutoring in graduate school at Columbia, I strove to teach my students in the same way as he taught me. His class was probably the only thing for which it was worth it to get up at 7 am.\\

I would also like to thank my closest coworkers in the Columbia group, including Kazuhiro Terao, David Caratelli, Georgia Karagiorgi, Leslie Camilleri, Vic Genty, Rachel Carr, and others I may have forgotten to include here. You provided me with the right combination of technical coding expertise and particle physics knowledge I needed to accomplish my goal of receiving my doctorate. It was a pleasure working along side each of you, and I am grateful to have shared the responsibility of driving the vans full of chatty summer students back and forth to Irvington each summer.\\

Additionally, I would like to thank the MicroBooNE collaboration as a whole. I enjoyed working with my coworkers in Wilson Hall at Fermilab; the opportunity to walk down the hall to ask your physics question to a world-leading expert on that topic is one I didn't take for granted. On the tenth floor, I found the friendly yet driven work environment to be a good fit for me. It was nice to take a break from coding to solve a Rubik's cube with a friend or talk shop over some Fermilab cafeteria food at lunch time. Moving from New York to Chicago to work at Fermilab full time was a decision I did not regret.\\

I would like to thank my family for their constant support outside of physics. My mother and father have always been there for me throughout my entire life, and their support continued during my (notably more curmudgeonly) years in graduate school.\\

Lastly, I would like to thank my girlfriend Carolyn for agreeing to quit her job and move to Chicago with me. Together we've made a home and a life together in Oak Park, and adopting our Labrador retriever puppy Rosie was the best decision we've ever made. Carolyn kept me sane throughout my time in graduate school. I wouldn't be where I am today without her.